Demystifying the Computer Science PhD Admission in the US\\{\large A Guide for International Students

### 2023-11-25 demystify.tex
update

@@

% \subsection{Outline of a LOR}\label{sec:lor-outline}

@@

\subsection{Tenured, Tenure Track, Teaching,  Assistant Profs., Associate Profs, and O
ther Fancy Academic Titles}\label{sec:faculty-types}

@@

>>>>

\section{References}
\begin{itemize}
    \item \href{https://parentheticallyspeaking.org/articles/us-cs-phd-faq/}{Getting a Computer Science PhD in the USA} by Shriram Krishnamurthi
\end{itemize}

@@

\subsection{References}
\begin{itemize}
\item \href{http://www.pl-enthusiast.net/2022/10/03/how-to-write-a-grad-school-personal-statement/}{How to Write a Grad School Personal Statement} by Mike Hicks, 10/03/22
\end{itemize}
% \subsection{Outline of a LOR}\label{sec:lor-outline}

@@

\subsection{Tenured, Tenure Track, Teaching,  Assistant Profs., Associate Profs, and Other Academic Titles}\label{sec:faculty-types}

@@

\subsubsection{References}
\begin{itemize}
    \item \href{https://yonatanbisk.com/emailing_professors.html}{Emailing Professors} by Yonatan Bisk
\end{itemize}
